---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# nutils

<!-- badges: start -->
<!-- badges: end -->

The package *nutils* contains two kinds of utilities.

1. Those that I found useful particularly in early debugging 'scaffolding'

    * `catln`  -- just cat with a `newline` appended, analogous to python3 `print()`. Name inspired by venerable Pascal `writeln`.
    
    * `showvars` -- show variable names and print its type and contents.

2. A couple of functions that interface with the mac 
    * macopen - open a Mac folder or file in Finder or in the file's default application.
    
    * macedit - open a text file in Mac TextEdit app.


## Installation

You can install the latest commit from [GITHUB](https://github.com/) with:
`devtools:install_github("tnearey/nutils")`


## Example


```{r example}
library(nutils)
catln('a',"the banana is in the cupboard")
x=1
y="Why not"
lst=list('x'=x,'y'=y,fred=data.frame(x=x,y=y,z="Not me"))
showvars(x,y,lst)
```




